\section{Drivers for loading unfolding pull data}
\label{sec:hooke:drivers}

\Hooke\ supports a number of different SMFS data formats, including
Hemingway\citep{materassi09}, JPK's \citetalias{force-robot}, Asylum's
MFP3D\citep{mfp-3d}, Bruker's \citetalias{picoforce}, and my
\unfoldprotein\ (\cref{sec:pyafm:unfold-protein}) formats.  The
drivers are responsible for loading curve data into a standardized
format so that plugins can work with data from any source.  Drivers
can determine if they are capable of reading a particular file, so if
you need to analyze a directory full of curve files in a number of
formats, you can just point Hooke at the directory and it will pick
the appropriate driver for each curve.

After loading and parsing the data, drivers return a list of scaled
\emph{blocks} and a dictionary\footnote{
  Python dictionaries are hash tables, which allow you to easily
  access arbitrary data if you know the key under which it was stored.
} of metadata.  Each block corresponds to a different phase of the
experiment; standard unfolding experiments have an approach block and
a retraction block.  The piezo position and cantilever deflection data
in each block is scaled by the driver into meters, but further
processing (e.g. the conversion of cantilever position to a chain
tension in newtons) is carried out by plugins.  The metadata
dictionary includes standard keys for information that is required for
the analysis (e.g.~the calibrated spring constant in N/m).  If the
driver can parse any additional metadata from the file, it adds it to
the dictionary using non-standard keys.  You can use this auxilliary
metadata to perform subsequent analysis (e.g.~``give me all the curves
that were recorded in \texttt{PBS + 0.5M CaCl2}'').
