\section{Sample preparation}
\label{sec:sample-preparation}

In mechanical unfolding experiments, one end of the protein is bound
to a substrate and the other binds to the AFM tip.  This allows you to
stretch the protein by increasing the tip-substrate distance using the
piezo.  A common approach is to synthesize proteins with cystine
residues on one end (\cref{eq:I27}) and allow the cystines to bind to
a gold surface\citep{carrion-vazquez99b,carrion-vazquez00,ulman96}.

We prepare gold-surfaces by sputtering gold onto freshly cleaved mica
sheets in a vacuum.  The mica keeps the gold surface protected from
contamination until it is needed.  In order to mount the gold on our
AFM, we glue glass coverslips to the gold using a two part epoxy. %(TODO)
Instead of using mica to protect the gold surface, some labs
evaporate the gold directly onto the coverslips immediately before
running an experiment\citep{carrion-vazquez99b}.

When it is time to deposit proteins on the surface, we peel a
coverslip off the gold-coated mica, exposing the gold surface that had
previously been attached to the mica.  We dispense $5\U{$\mu$L}$ of
I27 solution ($65\U{g/$\mu$L}$) on the freshly-exposed gold, followed
by $5\U{$\mu$L}$ of phosphate buffered saline (PBS).  We allow the
protein to bind to the gold surface for 30 mintues and then load the
coated coverslips into our AFM fluid cell. There are a number of
similar PBS recipes in common
use\citep{florin95,carrion-vazquez00,lo01,brockwell02}, but our PBS is
diluted from 10x PBS stock composed of $1260\U{mM}$ NaCl, $72\U{mM}$
\diNaHPO, and $30\U{mM}$ \NadiHPO\citep{chyan04}.
%
\index{Phosphate buffered saline (PBS)}
\nomenclature[text ]{PBS}{Phosphate buffered saline.}

As an alternative to binding proteins to gold, others have used
EGTA\citep{kellermayer03},
Ni-NTA\citep{schmidt02,itoh04,sakaki05,berkemeier11}, or silanized
glass\citep{sundberg03,ma10}.  Some groups have also functionalized
the cantilever tips by coating them with molecules designed to bind to
the protein\citep{lee05}.  Of these, a Ni-NTA coating is the most
popular\citep{schmitt00}.
%
\nomenclature[text ]{EGTA}{Ethylene glycol tetraacetic acid}
