\iffinal{}{\newpage}

\begin{vita}

{\Large\bf Austen M. Groener}

\singlespacing
{\large\bf Education}
\begin{itemize} \itemsep -2pt
\item Drexel University, Philadelphia, Pennsylvania USA
	\vspace{-2pt}
	\begin{itemize} \itemsep -2pt
		\item Ph.D., Physics, September 2015
		\item M.S., Physics, June 2011
	\end{itemize}
	\vspace{-2pt}
\item Hartwick College, Oneonta, New York USA
	\vspace{-2pt}
	\begin{itemize} \itemsep -2pt
		\item B.A., Physics, May 2009
	\end{itemize}
\end{itemize}

{\large\bf Publications}
\begin{itemize} \itemsep -2pt
	\item ``The Galaxy Cluster Concentration-Mass Scaling Relation", 2015
	\item ``Shape Profiles and Orientation Bias for Weak and Strong Lensing Cluster Halos", \href{http://dx.doi.org/10.1088/0004-637X/795/2/153}{ApJ, 795, 2}, 2014
\end{itemize}

{\large\bf Awards}
\begin{itemize} \itemsep -2pt
\item Drexel University Outstanding Teaching Assistant Honorable Mention, 2012
\item Drexel College of Arts and Sciences Research Award, 2011
\item Hartwick College Service Award, 2009
\item Hartwick College Faculty Scholar, 2008
\end{itemize}


{\large\bf Teaching Experience}

\begin{itemize} \itemsep -2pt

\item {\bf Grader.} Physics 432/532: Cosmology, Drexel University

\item {\bf Grader.} Physics 631: General Relativity, Drexel University

\item {\bf Teaching Assistant/Telescope Operator.} Physics 232: Observational Astronomy,
  Drexel University, {\it The Lynch Observatory}

\item {\bf Teaching Assistant.} Physics 113, 114, 115: Contemporary
  Physics I, II, III, Drexel University

\item {\bf Teaching Assistant.} Physics 152, 153, 154: Introductory
  Physics I, II, III, Drexel University

\item {\bf Teaching Assistant.} Physics 135: How Things Work,
  Drexel University

\item {\bf Teaching Assistant.} Physics 101, 102: Fundamentals of
  Physics I, II, Drexel University

\item {\bf Supplemental Instructor/Private Tutor.} Physics 201, 202: General Physics I, II,
  Hartwick College

\item {\bf Supplemental Instructor/Private Tutor.} Physics 163: General Astronomy,
  Hartwick College

\end{itemize}


{\large\bf Public Outreach}
\begin{itemize} \itemsep -2pt
	\item \textbf{Dragons Code} \hfill \textit{October 2014 to March 2015}
	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2009 to December 2014}
\end{itemize}

\end{vita}